%______________________________________________________________________________________________________________________
% @brief    LaTeX2e Resume for Kathryn D. Huff

\documentclass[margin,line]{resume}
\usepackage{bibentry}
\makeatletter\let\saved@bibitem\@bibitem\makeatother
\usepackage{hyperref}
\makeatletter\let\@bibitem\saved@bibitem\makeatother
\usepackage{doi}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=cyan,
}
\urlstyle{same}
\usepackage{xspace}
%\textheight=10.75in
\newcommand{\Cyclus}{\textsc{Cyclus}\xspace}%

% Trying to bold my name in the bib
\usepackage{xstring}
\def\FormatName#1{%
  \IfSubStr{#1}{Huff}{\textbf{#1}}{#1}%
}


%______________________________________________________________________________________________________________________
\begin{document}
\name{\Large Kathryn D. Huff}
\begin{resume}

%\bibliographystyle{katyunsrt}
\bibliographystyle{abbrvurl-huff}
\nobibliography{cv}

    % Contact Information
    \section{\mysidestyle Contact\\Information}
    Blue Waters Assistant Professor \hfill mobile: (281) 734-1342 \vspace{0mm}\\\vspace{0mm}%
        \textsl{University of Illinois, Urbana-Champaign}
        \hfill e-mail: katyhuff@gmail.com            \vspace{0mm}\\\vspace{0mm}%
    \textsl{Nuclear, Plasma, and Radiological Engineering}
        \hfill website: katyhuff.github.com     \vspace{0mm}\\\vspace{0mm}%
    \textsl{Affiliate Faculty, National Center for Supercomputing Applications}           \vspace{0mm}\\\vspace{0mm}%
    \textsl{Affiliate Faculty, Computational Science and Engineering}           \vspace{0mm}\\\vspace{-4.5mm}%

    %__________________________________________________________________________________________________________________
    % Resume Objective
    %\section{\mysidestyle Objective}
                %Seeking research and teaching opportunities in nuclear engineering and scientific computation.%
    %__________________________________________________________________________________________________________________
    % Research Interests
    \section{\mysidestyle Research\\Interests}
                Advanced nuclear reactors and fuel cycles, multi-physics
                simulation, nuclear fuel cycle analysis,
                scientific computation.
                %
    %__________________________________________________________________________________________________________________
    % Academic Appointments
    %           \vspace{-2mm}
    %\section{\mysidestyle Academic\\Appointments}
    %           \vspace{-2mm}\\\vspace{-3mm}%
    %__________________________________________________________________________________________________________________
    % Education
    \section{\mysidestyle PhD}
    \textbf{University of Wisconsin - Madison}, \textsc{Nuclear Engineering}\hfill \textbf{ Aug 2008 -- Aug 2013}\vspace{-3mm}\\\vspace{-1mm}%
    \begin{list2}
        \item An Integrated Used Fuel Disposition and Generic Repository Model for Fuel Cycle Analysis
        \item Advisor:  Professor Paul P.H. Wilson
    \end{list2}\vspace{-1.5mm}
    \section{\mysidestyle BA}
    \textbf{University of Chicago}, \textsc{Physics}\hfill\textbf{Aug 2004 -- Jun 2008}\vspace{-3mm}\\\vspace{-1mm}%
    \begin{list2}
        \item Celestial Gain Calibrations of QUIET Telescope Polarimeters
    \end{list2}\vspace{-1.5mm}
    %__________________________________________________________________________________________________________________
    % Research Experience
    \section{\mysidestyle Research\\Experience}
    \textbf{University of Illinois at Urbana-Champaign}, Urbana, IL\\
                \textsl{Assistant Professor, Nuclear Plasma and Radiological Engineering} \hfill \textbf{Aug 2016 -- Present}\\
                \textsl{Blue Waters Asst. Prof., National Center for Supercomputing Applications} \hfill \textbf{Aug 2016 -- Present}\\
                Principal investigator, advanced reactors and fuel cycles group.

    \textbf{University of California - Berkeley, NE Dept.}, Berkeley, CA \\
                \textsl{Postdoctoral Scholar, Nuclear Science and Security Consortium} \hfill \textbf{Sep 2013 -- Jul 2016}\\
                \textsl{Data Science Fellow, Berkeley Institute for Data Science} \hfill \textbf{Aug 2014 -- Jul 2016}\\
                Developing computational tools and multiphysics models for advanced reactor safety analysis.

    \textbf{Argonne National Laboratory}, Argonne, IL \hfill \textbf{Jun 2011 -- Aug 2013}\\
                \textsl{Laboratory Graduate Research Appointee, Used Fuel Disposition Campaign}\\
                Developed a used fuel disposition and generic repository computational model.

    \textbf{University of Wisconsin - Madison, NEEP Dept.}, Madison, WI \hfill \textbf{Jun 2008 -- Aug 2013}\\
                \textsl{Graduate Research Assistant, Computational Nuclear Engineering Research Group}\\
                Developed and applied \Cyclus, a nuclear fuel cycle systems analysis tool.

    \textbf{Idaho National Laboratory}, Idaho Falls, ID \hfill \textbf{Jun -- Aug 2010}\\
                \textsl{Graduate Research Assistant, Systems Analysis Campaign}\\
                Developed software functions and requirements for the Fuel Cycle Simulator concept.

    \textbf{Kavli Institute For Cosmological Physics}, Chicago, IL \hfill \textbf{Jan 2005 -- Jun 2008}\\
                \textsl{Research Assistant, Laboratory for Astrophysics and Space Research}\\
                Programmed \& machined instrumentation. Planned protocol for QUIET polarimeter calibration.

    \textbf{Universidad de Chile, Physics Dept.}, Santiago, Chile \hfill \textbf{Jun -- Sep 2006}\\
                \textsl{Research Assistant, Chicago-Chile Research Exchange Program}\\
                 Constructed and operated a far-from-equilibrium granular
                 materials experiment.

    \textbf{Los Alamos Neutron Science Center}, Los Alamos, NM \hfill \textbf{Jun -- Sep 2004}\\
                \textsl{Research Assistant, LANSCE-3} \hfill \textbf{May -- Aug 2003}\\
                Applied digital filtration algorithms and MCNPX models to experimental data.
    %__________________________________________________________________________________________________________________
    % Honors and Awards
    \section{\mysidestyle Honors and\\Awards}
                Stanley H. Pierce Award, UIUC Engineering Council \hfill \textbf{2019}\vspace{.5mm}\\%
                American Nuclear Society, Oestmann Professional Women's Achievement Award\hfill \textbf{2017}\vspace{.5mm}\\%
                AE3, Collins Scholars Program Graduate\hfill \textbf{2017}\vspace{.5mm}\\%
                NPRE, Students Award for Excellence in Undergraduate Teaching \hfill \textbf{2017}\vspace{.5mm}\\%
                UIUC, Teachers Ranked as Excellent \hfill \textbf{F 2016, S 2020}\vspace{.5mm}\\%
                American Nuclear Society, Young Member Excellence Award                         \hfill \textbf{2016}\vspace{.5mm}\\%
                National Energy Research Scientific Computing Allocation, Senior Investigator     \hfill \textbf{2015--2016}\vspace{.5mm}\\%
                Data Science Fellowship, Berkeley Institute for Data Science, UC Berkeley     \hfill \textbf{2014--2016}\vspace{.5mm}\\%
                Nuclear Science and Security Consortium Postdoctoral Fellowship, UC Berkeley  \hfill \textbf{2013--2016}\vspace{.5mm}\\%
                DOE Office of Science Laboratory Graduate Appointment, Argonne National Lab   \hfill \textbf{2011--2013}\vspace{.5mm}\\%
                Roy G  Post Foundation Nuclear Waste Management Graduate Scholarship                \hfill \textbf{2011}\vspace{.5mm}\\%
                John Randall Memorial Scholarship, American Nuclear Society FCWMD                   \hfill \textbf{2009}\vspace{.5mm}\\%
                J.A  McDeavitt Scholarship, University of Chicago, Chicago, IL                 \hfill\textbf{2007--2008}\vspace{.5mm}\\%
                University Scholar Award, University of Chicago, Chicago, IL                   \hfill\textbf{2004--2008}\vspace{.5mm}\\%
                Los Alamos Distinguished Student Performance Award, Los Alamos National Lab                         \hfill\textbf{2004}%
    %__________________________________________________________________________________________________________________
    % Grants Awarded
    \section{\mysidestyle Grants\\Awarded}
    \textbf{Evaluation of micro-reactor requirements and performance in an 
    existing \\
    well-characterized micro-grid} \hfill \textsl{Period:} 2020--2022\\
    \textsl{Source:} DOE-NEUP \hfill \textsl{Award Total:} \textbf{\$800,000}\\
    \textsl{Role:} Co-PI \hfill \textsl{Huff Allocation:} \textbf{\$265,000}\vspace{2mm}\\%
    \textbf{Enabling Load Following Capability in the Transatomic Power MSR} \hfill \textsl{Period:}
    2018--2021\\
    \textsl{Source:} ARPA - E - MEITNER \hfill \textsl{Award Total:} \textbf{\$999,694}\\
    \textsl{Role:} \textbf{Principal Investigator} \hfill \textsl{Huff Allocation:} \textbf{\$205,000}\vspace{2mm}\\%
    \textbf{US Research Software Sustainability Institute (URSSI)} \hfill \textsl{Period:}
    2017--2018\\
    \textsl{Source:} NSF - OAC - SI2 - S2I2 Conceptualization \hfill \textsl{Award Total:} \$499,999\\
    \textsl{Role:} Senior Personnel\hfill \textsl{Huff Allocation:} \textbf{N/A}\vspace{2mm}\\%
    \textbf{Dynamic Transition Analysis with TIMES} \hfill \textsl{Period:}
    2018--2019\\
    \textsl{Source:} I$^2$CNER \hfill \textsl{Award Total:} \$76,359\\
    \textsl{Role:} Co-PI \hfill \textsl{Huff Allocation:} \textbf{\$76,359}\vspace{2mm}\\%
    \textbf{Investigation of Agricultural Uses of Nuclear Waste Heat} \hfill \textsl{Period:} 2017--2018\\
    \textsl{Source:} Exelon \hfill \textsl{Award Total:} \$151,257\\
    \textsl{Role:} Co-PI \hfill \textsl{Huff Allocation:} \textbf{\$11,678}\vspace{2mm}\\%
    \textbf{Consortium for Verification Technology} \hfill \textsl{Period:} 2015--2020\\
    \textsl{Source:} NNSA Office of DNN R\&D \hfill \textsl{Award Total:} \$25,000,000\\
    \textsl{Role:} UIUC PI, CVT Investigator  \hfill \textsl{Huff Allocation:} \textbf{\$347,000}\vspace{2mm}\\%
    \textbf{Consortium for Nonproliferation Enabling Capabilities} \hfill \textsl{Period:} 2014--2019\\
    \textsl{Source:} NNSA Office of DNN R\&D \hfill \textsl{Award Total:} \$25,000,000\\
    \textsl{Role:} UIUC PI, Thrust Area Lead  \hfill \textsl{Huff Allocation:} \textbf{\$648,000}\vspace{2mm}\\%
    \textbf{Collaborative, Open-Source Curriculum Development} \hfill \textsl{Period:} 2017--2018\\
    \textsl{Source:} UIUC Strategic Instructional Innovations Program\hfill \textsl{Award Total:} \$19,347\\
    \textsl{Role:} PI \hfill \textsl{Huff Allocation:} \textbf{\$13,000}\vspace{2mm}\\%
    \textbf{REU Site: INCLUSION at U. Illinois} \hfill \textsl{Period:}
    2017--2020\\
    \textsl{Source:} NSF - ACI \hfill \textsl{Award Total:} \$380,036\\
    \textsl{Role:} Senior Personnel\hfill \textsl{Huff Allocation:} \textbf{N/A}\vspace{2mm}\\%
    \textbf{Demand-Driven Cycamore Archetypes} \hfill \textsl{Period:} 2016--2019\\
    \textsl{Source:} DOE, NEUP R\&D \hfill \textsl{Award Total:} \$800,000\\
    \textsl{Role:} Co-PI \hfill \textsl{Huff Allocation:} \textbf{\$395,066}\vspace{2mm}\\%
%    \section{\mysidestyle Recently\\Submitted\\Proposals}
%    \begin{graytext}
%    \textbf{Repurposing NPPs for Optimum Utilization and Energy Recovery} \hfill \textsl{Period:} 2017--2020\\
%    \textsl{Source:} DOE, NEUP IRP \hfill \textsl{Award Total:} \$3,000,000\\
%    \textsl{Role:} Co-PI \hfill \textsl{Huff Allocation:} \textbf{$~\$$300,000}\vspace{2mm}\\%
%    \textbf{Benchmark Demonstration of the NEAMS Workbench} \hfill \textsl{Period:} 2017--2021\\
%    \textsl{Source:} DOE, NEUP R\&D \hfill \textsl{Award Total:} \$800,000\\
%    \textsl{Role:} PI \hfill \textsl{Huff Allocation:} \textbf{\$320,000}\vspace{2mm}\\%
%    \textbf{A Novel Small Advanced Reactor with FCM Fuel} \hfill \textsl{Period:} 2017--2019\\
%    \textsl{Source}: DOE, NEUP R\&D \hfill \textsl{Award Total:} \$400,000\\
%    \textsl{Role: Co-PI} \hfill \textsl{Huff Allocation:} \textbf{\$160,000}\vspace{2mm}\\%
%    \textbf{Chemical, TH, \& Neutronic Coupled Capability for MSRs} \hfill \textsl{Period:} 2018--2021\\
%    \textsl{Source: Idaho National Laboratory LDRD} \hfill \textsl{Award Total:} \$1,125,000\\
%    \textsl{Role: Co-Investigator} \hfill \textsl{Huff Allocation:} \textbf{\$300,000}\vspace{2mm}\\%
%    \textbf{Conceptualizing a US Research Software Sustainability Institute} \hfill \textsl{Period:} 2018--2019\\
%    \textsl{Source: NSF SI2-S2I2} \hfill \textsl{Award Total:} \$500,000\\
%    \textsl{Role: Senior Personnel} \hfill \textsl{Huff Allocation:} \textbf{N/A}\\
%    \end{graytext}
    %__________________________________________________________________________________________________________________
    % Books YO!!!
               \vspace{-2mm}
    \section{\mysidestyle Books}
      \begin{bibenum}
      \item \bibentry{scopatz_effective_2015}
      \end{bibenum}

    \section{\mysidestyle Book\\Chapters}
      \begin{bibenum}
      \item \bibentry{huff_chapter_2019}
      \item \bibentry{huff_case_2017}
      \item \bibentry{huff_lessons_2017}
      \end{bibenum}

    \section{\mysidestyle Journal\\Publications}
    %\section{\mysidestyle Refereed\\Journal\\Publications} % also, vspace below
      \begin{bibenum}
      \item \bibentry{ashraf_strategies_2020}
      \item \bibentry{miernicki_nuclear_2020}
      \item \bibentry{chee_demand-driven_2020}
      \item \bibentry{bae_deep_2020}
      \item \bibentry{ashraf_whole_2020}
      \item \bibentry{kamuda_comparison_2020}
      \item \bibentry{bae_synergistic_2019}
      \item \bibentry{bae_standardized_2019}
      \item \bibentry{rykhlevskii_modeling_2019}
      \item \bibentry{lindsay_introduction_2018}
      \item \bibentry{smith_journal_2018}
      \item \bibentry{lindsay_moltres_2018}
      \item \bibentry{allen_engineering_2017}
      \item \bibentry{huff_rapid_2017}
      \item \bibentry{andreades_design_2016}
      \item \bibentry{huff_fundamental_2016}
      \item \bibentry{wilson_best_2014}
      \item \bibentry{clerc_liquid-solid-like_2008}
      \end{bibenum}
      %\vspace{2mm} % add this back if you return to Refereed Journal..
      %\section{\mysidestyle Submitted}
      %\begin{bibenum}
      %\end{bibenum}
    \section{\mysidestyle Refereed\\Conference\\Proceedings}
    \begin{bibenum}
    %\item \bibentry{<++>}
    \item \bibentry{betzler_impacts_2019}
    \item \bibentry{chee_demonstration_2019}
    \item \bibentry{flanagan_methods_2019}
    \item \bibentry{park_safety_2019}
    \item \bibentry{rykhlevskii_fuel_2019}
    \item \bibentry{westphal_pyre_2018}
    \item \bibentry{smith_introducing_2017}
    \item \bibentry{smith_journal_2017}
    \item \bibentry{huff_current_2017}
    \item \bibentry{bae_benefits_2017}
    \item \bibentry{wang_coupled_2016}
    \item \bibentry{wang_sensitivity_2016}
    \item \bibentry{djokic_application_2015}
    \item \bibentry{huff_pyrk:_2015}
    \item \bibentry{krumwiede_design_2014}
    \item \bibentry{huff_cyclus_2013}
    \item \bibentry{gidden_agent-based_2013}
    \item \bibentry{huff_hydrologic_2013}
    \item \bibentry{huff_cyclus_2011}
    \item \bibentry{oliver_studying_2009}
    \item \bibentry{mujica_solid-liquid-like_2008}
    \item \bibentry{rochman_first_2005}
          % [paper]
    \end{bibenum}
    %__________________________________________________________________________________________________________________
    % Submitted Journal Publications
    %           \vspace{-2mm}
    %\section{\mysidestyle Submitted\\Journal\\Publications}
    %            Submitted Journal Publications \vspace{-2mm}\\\vspace{-3mm}%
    %__________________________________________________________________________________________________________________
    % Conference Publications
    \section{\mysidestyle Refereed\\Conference\\Abstracts}
    \begin{bibenum}
     \item \bibentry{dotson_optimal_2020}
     \item \bibentry{turkmen_single_2020}
     \item \bibentry{fairhurst_agosta_hydrogen_2020}
     \item \bibentry{fairhurst_agosta_hydrogen_2020-1}
     \item \bibentry{chaube_dynamic_2019}
     \item \bibentry{chee_demonstration_2019}
     \item \bibentry{park_safety_2019}
     \item \bibentry{rykhlevskii_impact_2019}
     \item \bibentry{hague_comparison_2019}
     \item \bibentry{chee_simulation_2019}
     \item \bibentry{westphal_signatures_2018}
     \item \bibentry{chee_validation_2018}
     \item \bibentry{bae_impact_2018}
     \item \bibentry{chaube_dynamic_2018}
     \item \bibentry{kamuda_comparison_2018}
     \item \bibentry{chee_numerical_2018}
     \item \bibentry{kissinger_simulating_2018}
     \item \bibentry{rykhlevskii_online_2017}
     \item \bibentry{rykhlevskii_full-core_2017}
     \item \bibentry{ridley_introduction_2017}
     \item \bibentry{bae_synergistic_2017}
     \item \bibentry{scopatz_modernizing_2015}
     \item \bibentry{bates_pyne_2014}
     \item \bibentry{huff_extensions_2014}
     \item \bibentry{huff_dynamic_2013}
     \item \bibentry{huff_numerical_2012}
     \item \bibentry{scopatz_pyne:_2012}
     \item \bibentry{gidden_once-through_2012}
     \item \bibentry{huff_key_2012}
     \item \bibentry{huff_cyclus_2011}
     \item \bibentry{huff_rapid_2011}
     \item \bibentry{huff_open_2011}
     \item \bibentry{huff_mox_2010}
     \item \bibentry{elmore_geniusv2_2009}
     \item \bibentry{huff_geniusv2_2009}
     \item \bibentry{huff_genius_2009}
    \item Rykhlevskii, A., \textbf{Huff, K.} ``Computational Tools for Advanced
            Molten Salt Reactor Simulation'', \textbf{Blue Waters Symposium},
            Sun River, OR, June 2018.
    \item Bae, J. W., \textbf{Huff, K.}, Singer,C. ``Synergistic Spent Nuclear Fuel Dynamics Within the European Union''
            \textbf{Transactions of the American Nuclear Society Winter Conference.}
            Washington, DC, November 2017.
    \item Rykhlevskii, A., Lindsay, A., \textbf{Huff, K.} ``Full-core analysis of thorium-fueled Molten Salt Breeder Reactor using the SERPENT 2 Monte Carlo code''
            \textbf{Transactions of the American Nuclear Society Winter Conference.}
            Washington, DC, United States, November 2017.
    \item Rykhlevskii, A., Lindsay, A., \textbf{Huff, K.} ``Online reprocessing simulation for thorium-fueled molten salt breeder reactor,''
            \textbf{Transactions of the American Nuclear Society Winter Conference.}
            Washington, DC, United States, November 2017.
    \item Ridley, G., Lindsay, A., and \textbf{Huff, K.} ``An
            Introduction To Moltres, an MSR Multiphysics Code.'' \textbf{Transactions
            of the American Nuclear Society Winter Conference}. Washington
            D.C., United States, November 2017.
      \item \textbf{Huff, K.}, Scopatz, A. ``Modernizing Computational Nuclear Engineering Education -- In the Open''
         \textbf{Transactions of the American Nuclear Society Winter Conference.}
         Washington, DC. November 2015.
      \item \textbf{Huff, K.}, Fratoni, M., Greenberg, H. ``Extensions to the CYCLUS Ecosystem in Support of Market-Driven Transition Capability''
         \textbf{Transactions of the American Nuclear Society Winter Conference.}
         Anaheim, CA. November 2014.
      \item Bates, C., Biondo, E., \textbf{Huff, K.}, Kiesling, K., Scopatz, A. ``PyNE Progress Report''
         \textbf{Transactions of the American Nuclear Society Winter Conference.}
         Anaheim, CA. November 2014.
      \item \textbf{Huff, K.}, Bara, A. ``Dynamic Determination of Thermal Repository Capacity For Fuel Cycle Analysis.''
         \textbf{Transactions of the American Nuclear Society Annual Conference.}
         Atlanta, GA. June 2013.
      \item \textbf{Huff, K.}, Nutt, M. ``Key Processes and Parameters in a Generic Clay Disposal System Model.''
         \textbf{Transactions of the American Nuclear Society Winter Conference.}
        San Diego, CA. November 2012.
        % [paper][talk]
      \item Scopatz, A.M., Romano, P.K., Wilson, P.P.H., \textbf{Huff, K.} ``PyNE: Python For Nuclear Engineering.''
         \textbf{Transactions of the American Nuclear Society Winter Conference.}
        San Diego, CA. November 2012.
        % [paper][talk]
      \item \textbf{Huff, K.}, Bauer, T. ``Numerical Calibration of an Analytical Generic Nuclear Repository Heat Transfer Model.''
         \textbf{Transactions of the American Nuclear Society Annual Conference.}
        Chicago, IL. June 2012.
        % [paper][talk]
      \item \textbf{Huff, K.}, Gidden, M., Wilson, P.P.H. ``Open architecture and modular paradigm of \Cyclus, a fuel cycle simulation code.''
         \textbf{Transactions of the American Nuclear Society Annual Conference.}
        Hollywood, FL. June 2011.
        % [paper][talk]
      \item \textbf{Huff, K.}, Scopatz, A., Preston, N., Wilson, P.P.H. ``Rapid Peer Education of a Computational Nuclear Engineering Skill Suite.''
         \textbf{Transactions of the American Nuclear Society Annual Conference.}
        Hollywood, FL. June 2011.
        % [paper][talk]
      \item \textbf{Huff, K.} ``\Cyclus: An Open, Modular, Next Generation Fuel Cycle Simulator Platform. ''
        (poster)  \textbf{Waste Management Symposium.} Phoenix, AZ. March
        2011.
        % [poster][award]
      \item \textbf{Huff, K.}, ``MOX Fuel Recipe Approximation Tests in GENIUSv2. ''
         \textbf{Proceedings of the American Nuclear Society Student Conference.}
        Ypsilanti, MI. April 2010.
        % [paper][talk]
      \item \textbf{Huff, K.}, Oliver, K., Wilson, P.P.H. ``GENIUSv2 Discrete Facilities/Materials Modeling of International
        Fuel Cycle Robustness. ''
         \textbf{Transactions of the American Nuclear Society Winter Conference.}
        Washington D.C. November 2009.
        % [paper][talk]
      \item \textbf{Huff, K.}, Wilson, P.P.H., Oliver, K. ``GENIUS Version 2: Modelling the Worldwide Nuclear Fuel Cycle.''
        (poster)  \textbf{eHub Conference.} University of Wisconsin -
        Madison. November 2009.
        % [poster]
    \end{bibenum}

    %__________________________________________________________________________________________________________________
    % Technical Reports
    \section{\mysidestyle Technical\\Reports}
    \begin{bibenum}
      \item Lindsay, A., \textbf{Huff, K.}. ``Coupled Multi-Physics of Advanced
              Molten Salt Nuclear Reactors.'' \textbf{National Center for
              Supercomputing Applications,} Blue Waters Annual Report,
              \url{https://bluewaters.ncsa.illinois.edu/liferay-content/document-library/BW_AR_2017.pdf}
              2017.
      \item Chee, G.J., Bae, J.W., \textbf{Huff, K.}, ``Numerical Experiments
              For Verifying Demand Driven Deployment Algorithms.''
              \textbf{Advanced Reactors and Fuel Cycles Report Series}, Nuclear Plasma and Radiological Engineering, University of Illinois.  Report
              UIUC-ARFC-2018-01,
              \url{https://arfc.npre.illinois.edu/research/reports/uiuc-arfc-2018-01.pdf}
              Apr.2018.
      \item Bae, J.W. \textbf{Huff, K.}, ``Non-algorithmic Capability Gaps for
              Cyclus and Cycamore Transition Analyses,'' \textbf{Advanced
              Reactors and Fuel Cycles Report Series}, Nuclear Plasma and
              Radiological Engineering, University of Illinois.  Report
              UIUC-ARFC-2017-02,
              \url{https://arfc.npre.illinois.edu/research/reports/uiuc-arfc-2017-02.pdf}
              Nov. 2017.
      \item Ridley, G., Lindsay, A., Turk, M., \textbf{Huff, K.}, ``Multiphysics
              Analysis of Molten Salt Reactor Transients,'' \textbf{Advanced
              Reactors and Fuel Cycles Report Series}, Nuclear Plasma and
              Radiological Engineering, University of Illinois.  Report
              UIUC-ARFC-2017-01,
              \url{https://arfc.npre.illinois.edu/research/reports/uiuc-arfc-2017-01.pdf}
              Aug. 2017.
      \item C. Andreades, A. T. Cisneros, J.K. Choi, A.Y.K. Chong, D. L.
              Krumwiede, L.R. Huddar, \textbf{K. Huff}, M. R. Laufer, M.O.
              Munk, R.O.  Scarlat, J. Seifried, N. Zweibaum, E. Greenspan, and
              P. F. Peterson, ``Technical Description of the ‘Mark 1’
              Pebble-Bed Fluoride-Salt-Cooled High-Temperature Reactor (PB-FHR)
              Power Plant,'' \textbf{U.C. Berkeley Nuclear Engineering}, Report
              UCBTH-14-002, 2014.
      \item \textbf{Huff, K.}, Nutt, W.M. ``FY12 Sensitivity Studies Using the UFD Clay Generic Disposal System Model.''
        \textbf{Argonne National Laboratory}. July 2012.
      \item \textbf{Huff, K.}, Bauer, T.H. ``Benchmarking a New Closed-Form Thermal Analysis Technique Against a Traditional
        Lumped Parameter, Finite-Difference Method'' \textbf{Argonne National Laboratory}. (FCRD-UFD-2012-000142). July 2012.
      \item \textbf{Huff, K.}, Dixon, B., Braase, L. ``Next Generation Fuel Cycle Simulator Functions and Requirements Document.''
        \textbf{Idaho National Laboratory} (FCRD-SYSA-2010-000110). July 2010.
        % [paper]
      \item \textbf{Huff, K.} ``Digital Filtering Application to the Lead Slowing Down
        Spectrometer.'' Los Alamos Neutron Science Center. August 2004.  %[paper][talk][award]
        (\textbf{awarded los alamos distinguished student award.})
      \item \textbf{Huff, K.} ``Excess Single Event Effects in the Second Chip of a Series.''
        Los Alamos Neutron Science Center. August 2003.
        %[paper][talk]
    \end{bibenum}
    %__________________________________________________________________________________________________________________
    % Other Publications
    \section{\mysidestyle Other\\Publications}
    \begin{bibenum}
      \item \textbf{Huff, K.} An Integrated Used Fuel Disposition and Generic Repository Model for Fuel Cycle Analysis.
        Ph.D. Dissertation--Nuclear Engineering and Engineering
        Physics. University of Wisconsin -- Madison.  August 2013.
      \item \textbf{Huff, K.} ``Celestial Calibrations of the Quiet Telescope.''
        Undergraduate Honors Thesis. University of Chicago. June 2008.
        % [paper][talk]
      \item Biris, O., Gracey, K., \textbf{Huff, K.}, Ng, W.K.
        ``An Analysis of the Consolidated Fuel Treatment Center Nuclear
        Reprocessing Initiative.''
        \textbf{Big Problems Energy Seminar. University of Chicago.} June 2008.
    \end{bibenum}
    %__________________________________________________________________________________________________________________
    % Software Products
    \section{\mysidestyle Software\\Products}
    \begin{bibenum}
    \item Carlsen, R., Flanagan, R., Gidden, M.,\textbf{Huff, K.,} Littell, J.,
            McGarry, M., Mouginot, B., Opotowsky, A., Scopatz, A., Skutnik, S.,
            and Wilson, P.. Cycamore v1.5.0. \textbf{figshare}, Nov 2016.
            \url{https://dx.doi.org/10.6084/m9.figshare.4312661.v1}.
    \item \textbf{Huff, K.}. ``PyRK v0.1'' \textbf{figshare.}
            \url{http://dx.doi.org/10.6084/m9.figshare.1540727}. September 2015.
    \item Carlsen, R., Flanagan, R., Gidden, M., \textbf{Huff, K.}, McGarry,
            M., Opotowsky, A., Scopatz, A., Wilson, P., and Xia, J.. Cyclus
            v1.3.0. \textbf{figshare}, July 2015.
            \url{http://dx.doi.org/10.6084/m9.figshare.1427429}.
      \item Bates, C., Biondo, E., Brachem, C., Carlsen, R., Cary, J., Davis, A., Dembia, C., Elfring, M., Flanagan, R., Gidden, M., Haines, T., Howland, J., Huff, B., \textbf{Huff, K.}, Jackson, S., Kiesling, K., Klebenow, M., Kuett, M., Manalo, K., M. McCormick, A. Opotowsky, C., Pavlovsky, R., Rabbani, M., Relson, E., Romano, P., Scopatz, A., Shriwise, P., Slaybaugh, R., Wilson, P., Xia, J., J. Zachman, C., and Zweig, M. ``PyNE v0.5.'' \textbf{github}.  github.com/pyne/pyne/releases/tag/0.5.0. April 2015.
      \item Carlsen, R., Gidden, M., \textbf{Huff, K.}, Opotowsky, A.,
      Rakhimov, O., Scopatz, A., and Wilson, P.. Cycamore v1.1.0.
      \textbf{figshare}, September 2014.
            \url{http://dx.doi.org/10.6084/m9.figshare.1174604}.
      \item Carlsen, R., Gidden, M., \textbf{Huff, K.}, Rakhimov, O., and
              Scopatz, A.. Cyclus v1.1.0. \textbf{figshare}, September 2014.
              \url{http://dx.doi.org/10.6084/m9.figshare.1174603}.
      \item Carlsen, R., Gidden, M., \textbf{Huff, K.}, Arrielle C. Opotowsky,
              Rakhimov, O., Scopatz, A., Zach Welch, and Wilson, P.. Cyclus
              v1.0.0. \textbf{figshare}, June 2014.
              \url{http://dx.doi.org/10.6084/m9.figshare.1041745}.
      \item Carlsen, R., Gidden, M., \textbf{Huff, K.}, Arrielle C. Opotowsky,
              Rakhimov, O., Scopatz, A., and Wilson, P.. Cycamore v1.0.0.
              \textbf{figshare}, June 2014.
              \url{http://dx.doi.org/10.6084/m9.figshare.1041829}.
    \end{bibenum}

    \section{\mysidestyle Media\\Coverage}
    \begin{bibenum}
        \item Silver, A. ``Microsoft's Purchase of GitHub Leaves Some Scientists Uneasy.'' \textbf{Nature News} In Focus, 558. June 21, 2018. \url{https://doi.org/doi: 10.1038/d41586-018-05426-0}.
        \item Coit, H., Holloway, M., Rice, M.,  Mumm, S. ``Professor Kathryn Huff on the Possibilities in NPRE.'' \textbf{NPRE YouTube Channel}. Urbana, IL: Illinois Engineering, March 14, 2018. \url{https://www.youtube.com/watch?v=w9d_QMW1hA4}.
        \item Bowne-Anderson, H. ``Data Science, Nuclear Engineering and the
                Open Source (with Katy Huff).'' \textbf{DataFramed Podcast}.
                March 5, 2018. \\\url{https://www.datacamp.com/community/podcast/data-science-nuclear-engineering}.
        \item Hacksworth, S. ``Nuclear Engineering Programs with Dr. Kathryn Huff.'' \textbf{YesCollege Podcast}. February 5, 2018. \url{https://yescollege.com/episode/kathryn-huff/}.
        \item Perkel, J. ``Democratic Databases: Science on GitHub.'' \textbf{Nature News}, Toolbox, 538, no. 7623. October 3, 2016. \url{https://doi.org/10.1038/538127a}.
        \item Tippmann, S. ``My Digital Toolbox: Nuclear Engineer Katy Huff on Version-Control Systems.'' \textbf{Nature News}, Toolbox: Q\&A, September 29, 2014. \url{https://doi.org/10.1038/nature.2014.16014}.
        \end{bibenum}
    %__________________________________________________________________________________________________________________
    % Invited Talks
    \section{\mysidestyle Invited\\Talks}
    %\textbf{<++>}, <++>, \emph{<++>}.  \hfill\textbf{<+mo+> <+date+>, <+yy+>}\\
    %\textbf{<++>}, <++>, \emph{<++>}.  \hfill\textbf{<+mo+> <+date+>, <+yy+>}\\
    \textbf{SIAM CSE 2019}, Spokane, WA, \emph{Invited Minisymposium Speaker}\hfill\textbf{Feb 25, 2019}\\
      \textbf{SciFOO}, Google X, \emph{Invited Camper}.  \hfill\textbf{Jun 23, 2018}\\
      \textbf{U. Illinois}, Hack Illinois, \emph{Keynote}.  \hfill\textbf{Feb 24, 2018}\\
      \textbf{U. Michigan}, Nuclear Engineering and Radiological Sciences \emph{Seminar}.  \hfill\textbf{Feb 9, 2018}\\
      \textbf{PyData}, Meetup, Ann Arbor, MI \emph{Invited Tech. Talk}.  \hfill\textbf{Feb 8, 2018}\\
      \textbf{Olin College of Engineering}, \emph{Seminar}.  \hfill\textbf{Oct 31, 2017}\\
      \textbf{Argonne National Laboratory}, NNSA Nuclear Nonproliferation, \emph{Seminar}.  \hfill\textbf{Sep 21, 2017}\\
      \textbf{SciPy 2017}, Scientific Python Conference, Austin, TX, \emph{Keynote}.  \hfill\textbf{Jul 12, 2017}\\
      \textbf{ANS Annual}, Young Members Group, Workforce Transition, \emph{Panel}.  \hfill\textbf{Jun 13, 2017}\\
      \textbf{ANS Annual}, Mathematics and Computation Division, Current Issues, \emph{Panel}.  \hfill\textbf{Jun 12, 2017}\\
      \textbf{Oak Ridge National Laboratory}, RPNSD, \emph{Seminar}.  \hfill\textbf{Jun 29, 2017}\\
      \textbf{PyCon 2017}, Portland, OR. \emph{Keynote}.  \hfill\textbf{May 19, 2017}\\
      \textbf{U. California, Davis}, Mechanical and Aerospace Engineering, \emph{Seminar}.  \hfill\textbf{April 20, 2017}\\
      \textbf{U. Illinois}, Computational Science and Engineering, \emph{Seminar}.  \hfill\textbf{Feb 2, 2017}\\
      \textbf{U. Illinois}, AE3 Lightning Symposium, \emph{Lightning Talk}.  \hfill\textbf{Mar 2, 2017}\\
      \textbf{U. Illinois}, Nuclear, Plasma, \& Radiological Engineering, \emph{Undergraduate Seminar}.  \hfill\textbf{Feb 14, 2017}\\
      \textbf{U. California, Berkeley}, Berkeley Institute for Data Science, \emph{Symposium}.  \hfill\textbf{Jan 27, 2017}\\
      \textbf{U. Illinois}, Informatics, \emph{Seminar}.  \hfill\textbf{Oct 13, 2016}\\
      \textbf{PyData 2016}, Chicago, IL. \emph{Keynote}.  \hfill\textbf{Aug 27, 2016}\\
      \textbf{Oak Ridge National Laboratory}, RPNSD, \emph{Seminar}.  \hfill\textbf{Mar 3, 2016}\\
      \textbf{U. Tennessee, Knoxville}, Nuclear Engineering, \emph{Seminar}.  \hfill\textbf{Mar 2, 2016}\\
      \textbf{Michigan State}, Computational, Mathematics, Science, and Engineering, \emph{Seminar}.  \hfill\textbf{Dec 15, 2015}\\
      \textbf{U. Illinois}, Nuclear, Plasma, \& Radiological Engineering, \emph{Seminar}.          \hfill\textbf{Dec 8, 2015}\\
      \textbf{SC15, Austin TX}, Python in High Performance Computing workshop, \emph{Keynote}.     \hfill\textbf{Nov 15, 2015}\\
      \textbf{U. Illinois}, National Center for Supercomputing Applications, \emph{Colloquium}.    \hfill\textbf{Nov 6, 2015}\\
      \textbf{North Carolina State University}, Nuclear Engineering, \emph{Colloquium}.            \hfill\textbf{Oct 15, 2015}\\
      %Lightning Plenary, Moore and Sloan Data Science Environment Summit.          \hfill\textbf{Oct 6, 2015}\\
      \textbf{Texas A\&M University}, Nuclear Engineering, \emph{Colloquium}.                      \hfill\textbf{ Sep 29, 2015}\\
      \textbf{Rensselaer Polytechnic Inst}, Mechanical and Nuclear Engineering, \emph{Colloquium}. \hfill\textbf{Sep 21, 2015}\\
      %Lightning Plenary, Data Science Faire. University of California Berkeley.    \hfill\textbf{May 5, 2015}\\
      \textbf{U. Washington}, What Can Academia Learn from Open Source?, \emph{Panel}.   \hfill\textbf{Feb 2, 2015}
      %Colloquium, Nuclear Engineering Department. University of California, Berkeley. \hfill\textbf{October 15, 2012}\\
    %__________________________________________________________________________________________________________________
    % Teaching Experience
    \section{\mysidestyle Engineering\\Teaching}
    \textbf{University of Illinois at Urbana-Champaign}\\
    \textsc{Dept. of Nuclear, Plasma, and Radiological Engineering}\\
               \textsl{NPRE 412, Nuclear Power Economics and Fuel Management} \hfill \textbf{Fall 2016}\\
               \mbox{ }~\hfill \textbf{Fall 2017}\\
               \textsl{NPRE 555, Reactor Theory I} \hfill \textbf{Spring 2018}\\
               \textsl{NPRE 247, Modeling Nuclear Energy Systems} \hfill \textbf{Fall 2018}\\
               \vspace{2mm}\\
    \textbf{University of California, Berkeley}, \textsc{Dept. of Nuclear Engineering} \hfill \textbf{Apr 1,3,22, 2015}\\
               \textsl{NE 155, Introduction to Numerical Simulations in Radiation Transport}\\
               Point Reactor Kinetics, Monte Carlo Methods
               \vspace{2mm}\\
    \textbf{University of California, Berkeley}, \textsc{Dept. of Nuclear Engineering} \hfill \textbf{Sep 11, 2014}\\
               \textsl{NE 255, Numerical Simulation in Radiation Transport}\\
               Best Practices in Computational Nuclear Engineering
               \vspace{2mm}\\
    \textbf{University of Wisconsin - Madison}, \textsc{Dept. of Nuclear Engineering} \hfill \textbf{Apr 1\&3, 2013}\\
               \textsl{NE 571, Economic and Environmental Aspects of Nuclear Energy}\\
               Nuclear Waste Repository Technology, Policy, and History
               \vspace{2mm}\\
    \textbf{University of Wisconsin - Madison}, \textsc{Dept. of Nuclear Engineering}\hfill \textbf{Sep 9\&11, 2009}\\
               \textsl{NE 406, Nuclear Reactor Analysis}\\
               UNIX Shell, Basic Scripting, Environment Variables, Permissions, Regular Expressions, Makefiles
               \vspace{2mm}\\
    \textbf{University of Wisconsin - Madison}, \textsc{Dept. of Nuclear
    Engineering} \hfill \textbf{Feb 10, 2010}\\
               \textsl{NE 506, Practicum in Monte Carlo Radiation Transport}\\
               UNIX Shell, Basic Scripting, Environment Variables, Permissions, Regular Expressions, Makefiles
               \vspace{2mm}

    \section{\mysidestyle Invited\\Scientific\\Computing\\Teaching}
    \textbf{SciPy Conference}, Austin, TX \hfill \textbf{Jul 6--7, 2015}\\
    Introductory Python For Scientific Software
               %python
               \vspace{2mm}\\
    \textbf{University of Split}, Split, Croatia \hfill \textbf{Sep 8--13, 2014}\\
    G-Node Advanced Scientific Programming in Python Summer School
               %UNIX Shell, Version Control, Databases, Scientific and Numerical Python
               \vspace{2mm}\\
    \textbf{SciPy Conference}, Austin, TX \hfill \textbf{Jun 25, 2013}\\
    Version Control and Unit Testing For Scientific Software
               %Version Control, Unit Testing
               \vspace{2mm}\\
    \textbf{University of Chicago, Graduate School}, Chicago, IL \hfill \textbf{Jan 12--13, 2013}\\
    Computational Literacy Workshop
               %UNIX Shell, Version Control, Databases, Python
               \vspace{2mm}\\
    \textbf{University of California, Berkeley}, Berkeley, CA \hfill \textbf{Oct 20--21, 2012}\\
    Department of Statistics Scientific Computing Workshop
               %UNIX Shell, Version Control, Databases, Python
               \vspace{2mm}\\
    \textbf{Lawrence Berkeley National Laboratory}, Berkeley, CA \hfill \textbf{Oct 17--18, 2012}\\
    Software Carpentry Python Workshop
               %Python, Nose, SciPy, NumPy, MatPlotLib
               \vspace{2mm}\\
    \textbf{International Center for Theoretical Physics}, Trieste, Italy \hfill \textbf{Feb 20--Mar 2, 2012}\\
    UNESCO/IAEA Advanced School on Scientific Software Development
               %Version Control, Python Basics, SciPy, NumPy, MatPlotLib, Fortran and C Binding with Python
               \vspace{2mm}\\
    \textbf{University of Toronto}, Toronto, ON, Canada \hfill \textbf{Nov 7--8, 2011}\\
    SciNet Consortium For High Performance Computing Software Carpentry Bootcamp
               %Version Control, Python, Testing, Auto-Documentation
               \vspace{2mm}\\
    \textbf{American Nuclear Society Winter Meeting}, Washington, D.C.  \hfill \textbf{Nov 1, 2011}\\
    Young Professionals Congress Hacker Within Scientific Computing Tutorial
               %Version Control, Testing, Auto-Documentation, Collaboration Tools
               \vspace{2mm}\\
    \textbf{Michigan State University}, East Lansing, MI \hfill \textbf{Jun 4--5, 2011}\\
    Institute for Cyber Enabled Research (iCER) and BEACON Center THW Bootcamp
               %UNIX Shell, Version Control, Text Editors, Databases, Auto-Documentation, Testing, Debugging

    \section{\mysidestyle Scientific\\Computing\\Teaching}
    \textbf{Berkeley Institute for Data Science}, Berkeley, CA \hfill \textbf{Jan 14--15, 2015}\\
    Managing Databases in SQL
               \vspace{2mm}\\
    \textbf{Berkeley Institute for Data Science}, Berkeley, CA \hfill \textbf{Jun 4--5, 2015}\\
    Testing for Scientific Software
               %Unit Testing
               \vspace{2mm}\\
    \textbf{Lawrence Berkeley National Laboratory}, Berkeley, CA \hfill \textbf{Apr 14--15, 2014}\\
    Women in Science and Engineering Bootcamp
               %UNIX Shell, Version Control, Databases, Scientific and Numerical Python
               \vspace{2mm}\\
    \textbf{The University of Chicago}, Chicago, IL \hfill \textbf{Apr 2--3, 2012}\\
    Software Carpentry Scientific Computing Workshop
               %UNIX Shell, Version Control, Databases
               \vspace{2mm}\\
    \textbf{The University of Wisconsin}, Madison, WI \hfill\textbf{Jan 12--14, 2011}\\
    The Hacker Within Software Carpentry Bootcamp
               %UNIX Shell, Version Control, Text Editors, Databases, Auto-Documentation, Testing, Debugging
               \vspace{2mm}\\
    \textbf{The University of Wisconsin}, Madison, WI \hfill \textbf{Jan 12--14, 2010}\\
    The Hacker Within Python Bootcamp
               %Data Structures, Flow Control, SciPy, NumPy, MatPlotLib, Fortran and C Binding with Python
               \vspace{2mm}\\
    \textbf{The University of Wisconsin}, Madison, WI \hfill \textbf{Mar 24--31, 2009}\\
    The Hacker Within C++ Bootcamp
               %Object Oriented Programming, Data Structures, C++ Basics
               \vspace{2mm}\\
    \textbf{The University of Wisconsin}, Madison, WI \hfill \textbf{Jan 12--15, 2009}\\
    University of Wisconsin, Hacker Within UNIX Bootcamp\\
               %UNIX Shell, Scripting, Environment, Permissions, Build Systems, Sed, Grep Awk, Common Utilities
    %__________________________________________________________________________________________________________________
    % Advising
    \section{\mysidestyle Postdoctoral\\Researchers}
    \makebox[0.3\textwidth][l]{\textsc{\underline{Name}}}
    \makebox[0.2\textwidth][l]{\textsc{\underline{Dates}}}
    \hfill\textsc{\underline{Role}}\\
    \makebox[0.3\textwidth][l]{\textbf{Mehmet Turkmen}}
    \makebox[0.2\textwidth][l]{2019--2020}
    \hfill Advisor\\
    \makebox[0.3\textwidth][l]{\textbf{Alexander Lindsay}}
    \makebox[0.2\textwidth][l]{2016--2017}
    \hfill Advisor\\
    \section{\mysidestyle Graduate\\Researchers}
    \makebox[0.3\textwidth][l]{\textsc{\underline{Name}}}
    \makebox[0.2\textwidth][l]{\textsc{\underline{Degree - Year}}}
    \hfill\textsc{\underline{Role}}\\
    \makebox[0.3\textwidth][l]{\textbf{Michael Cheng}}
    \makebox[0.2\textwidth][l]{MS - 2017}
    \hfill MS Second Reader\\
    \makebox[0.3\textwidth][l]{\textbf{Mark Kamuda}}
    \makebox[0.2\textwidth][l]{MS - 2017}
    \hfill MS Second Reader\\
    \makebox[0.3\textwidth][l]{\textbf{Mark Kamuda}}
    \makebox[0.2\textwidth][l]{PhD - 2019}
    \hfill PhD Advisor\\
    \makebox[0.3\textwidth][l]{\textbf{Gregory Westphal}}
    \makebox[0.2\textwidth][l]{MS - 2019}
    \hfill MS Advisor\\
    \makebox[0.3\textwidth][l]{\textbf{Erik Medhurst}}
    \makebox[0.2\textwidth][l]{MS - 2020}
    \hfill MS Advisor\\
    \makebox[0.3\textwidth][l]{\textbf{Andrei Rykhlevskii}}
    \makebox[0.2\textwidth][l]{PhD - 2020}
    \hfill PhD Advisor\\
    \makebox[0.3\textwidth][l]{\textbf{Jin Whan Bae}}
    \makebox[0.2\textwidth][l]{MS - 2019}
    \hfill PhD Advisor\\
    \makebox[0.3\textwidth][l]{\textbf{Sun Myung Park}}
    \makebox[0.2\textwidth][l]{PhD - (est. 2022)}
    \hfill PhD Advisor\\
    \makebox[0.3\textwidth][l]{\textbf{Anshuman Chaube}}
    \makebox[0.2\textwidth][l]{PhD - (est. 2022)}
    \hfill PhD Advisor\\
    \makebox[0.3\textwidth][l]{\textbf{Gwendolyn Chee}}
    \makebox[0.2\textwidth][l]{PhD - (est. 2022)}
    \hfill PhD Advisor\\
    \makebox[0.3\textwidth][l]{\textbf{Roberto Fairhurst-Agosta}}
    \makebox[0.2\textwidth][l]{PhD - (est. 2023)}
    \hfill PhD Advisor\\
    \makebox[0.3\textwidth][l]{\textbf{Zoe Richter}}
    \makebox[0.2\textwidth][l]{PhD - (est. 2023)}
    \hfill PhD Advisor\\
    \makebox[0.3\textwidth][l]{\textbf{Samuel Dotson}}
    \makebox[0.2\textwidth][l]{PhD - (est. 2024)}
    \hfill PhD Advisor\\
    \section{\mysidestyle Undergraduate\\Researchers}
    \makebox[0.3\textwidth][l]{\textsc{\underline{Name}}}
    \makebox[0.2\textwidth][l]{\textsc{\underline{Degree - Year}}}
    \hfill\textsc{\underline{Scholarships}}\\
    \makebox[0.3\textwidth][l]{\textbf{Jin Whan Bae}}
    \makebox[0.2\textwidth][l]{BS - 2017}
    \hfill NPRE Outstanding Undergrad Research\\
    \makebox[0.2\textwidth][l]{}
    \hfill ANS Best Student Fuel Cycle Presentation\\
    \makebox[0.3\textwidth][l]{\textbf{Kathryn Mummah}}
    \makebox[0.2\textwidth][l]{BS - 2017}
    \hfill Roy G. Post Foundation Scholarship\\
    \makebox[0.2\textwidth][l]{}
    \hfill ANS FCWMD Randall Scholar\\
    \makebox[0.3\textwidth][l]{\textbf{Eric Riewski}}
    \makebox[0.2\textwidth][l]{BS - 2017}
    \hfill \\
    \makebox[0.3\textwidth][l]{\textbf{GyuTae Park}}
    \makebox[0.2\textwidth][l]{BS - (est. 2018)}
    \hfill \\
    \makebox[0.3\textwidth][l]{\textbf{Yukun Tan}}
    \makebox[0.2\textwidth][l]{BS - (est. 2018)}
    \hfill Students Pushing Innovation\\
    \makebox[0.3\textwidth][l]{\textbf{Louis Kissinger}}
    \makebox[0.2\textwidth][l]{BS - (est. 2019)}
    \hfill \\
    \makebox[0.3\textwidth][l]{\textbf{Xin Wen}}
    \makebox[0.2\textwidth][l]{BS - (est. 2018)}
    \hfill Students Pushing Innovation\\
    \makebox[0.3\textwidth][l]{\textbf{Daniel Chu}}
    \makebox[0.2\textwidth][l]{BS - (est. 2020)}
    \hfill \\
    \makebox[0.3\textwidth][l]{\textbf{Tyler Kennelly}}
    \makebox[0.2\textwidth][l]{BS - (est. 2019)}
    \hfill \\
    \makebox[0.3\textwidth][l]{\textbf{Bradley Ellis}}
    \makebox[0.2\textwidth][l]{BS - (est. 2019)}
    \hfill \\
    \makebox[0.3\textwidth][l]{\textbf{Adam Pichman}}
    \makebox[0.2\textwidth][l]{BS - (est. 2019)}
    \hfill \\
    \makebox[0.3\textwidth][l]{\textbf{Zo{\"e} Richter}}
    \makebox[0.2\textwidth][l]{BS - (est. 2018)}
    \hfill \\

    \section{\mysidestyle Visiting\\Researchers}
    \makebox[0.3\textwidth][l]{\textsc{\underline{Name}}}
    \makebox[0.2\textwidth][l]{\textsc{\underline{Dates}}}
    \hfill\textsc{\underline{Level - Institution}}\\
    \makebox[0.3\textwidth][l]{\textbf{Gavin Ridey}}
    \makebox[0.2\textwidth][l]{2017}
    \hfill BS--University of Tennessee, Knoxville\\
    \makebox[0.3\textwidth][l]{\textbf{Aditya Bhosale}}
    \makebox[0.2\textwidth][l]{2017}
    \hfill BS - IIT, Bombay \\
    \makebox[0.3\textwidth][l]{\textbf{Snehal Chandan}}
    \makebox[0.2\textwidth][l]{2017}
    \hfill BS - IIT, Bombay\\
    %__________________________________________________________________________________________________________________
    % Computer Skills
    \section{\mysidestyle Scientific\\Computing\\Skills}
                \textbf{Languages} \hfill bash/csh, C++, FORTRAN, Perl, Python, XML\vspace{.5mm}\\%
                \textbf{Build Systems} \hfill make, CMake, automake\vspace{.5mm}\\%
                \textbf{Databases} \hfill HDF5, SQL\vspace{.5mm}\\%
                \textbf{Test Frameworks} \hfill CTest, GoogleTest, nose\vspace{.5mm}\\%
                \textbf{Version Control} \hfill cvs, git, hg, svn\vspace{.5mm}\\%
                \textbf{Other Tools} \hfill Doxygen, Sphinx, GoldSim, \LaTeX, Mathematica, MatLab, MCNP, MOOSE\vspace{.5mm}%
    %__________________________________________________________________________________________________________________
    % Professional, Student Organizations


    \section{\mysidestyle Editing and\\Reviewing}

    \textbf{Editorial Board} \hfill \emph{Journal of Open Source Software} \textbf{2016 -- present}\\%
     \mbox{}~\hfill \emph{Journal of Open Source Education} \textbf{2018 -- present}\\%
                    \mbox{}~\hfill \emph{Nuclear Technology} \textbf{2018 -- present}\vspace{2mm}\\%
                    \mbox{}~\hfill \emph{Nuclear Engineering and Design} \textbf{2020 -- present}\vspace{2mm}\\%
                    \mbox{}~\hfill \emph{Papers in Physics} \textbf{2020 -- 2023}\vspace{2mm}\\%
                    \mbox{}~\hfill \emph{Proceedings of the SciPy Scientific Python Conference} \textbf{2013, 2015, \& 2017}\vspace{2mm}\\%
    \textbf{Manuscript Referee}~\hfill\emph{Annals of Nuclear Energy}\\%
                            \mbox{}~\hfill \emph{Journal of Nuclear Energy Science and Power Generation Technology} \\%
                            \mbox{}\hfill \emph{Nuclear Engineering and Design}\\%
                            \mbox{}~\hfill\emph{Nuclear Science and Engineering}\\%
                            \mbox{}~\hfill\emph{Nuclear Technology}\\%
                            \mbox{}~\hfill\emph{Progress in Nuclear Energy}\vspace{2mm}\\%
    \textbf{Grant Proposal Referee} \hfill \emph{Dept. of Energy Nuclear Energy University Programs}\\%
                            \mbox{}~\hfill\emph{Dept. of Energy Technology Commercialization Fund}\\%
                            \mbox{}~\hfill\emph{Blue Waters Fellows Program}\vspace{2mm}\\%
                            \mbox{}~\hfill\emph{Alfred P. Sloan Foundation}\vspace{2mm}\\%
    \textbf{Book Proposal Referee} \hfill\emph{O'Reilly Media}\\%
                            \mbox{}\hfill\emph{Elsevier}\vspace{2mm}\\%
    \section{\mysidestyle Professional\\Service}
                \textbf{Chair}, Nonproliferation and Policy Division, ANS  \hfill \textbf{2020--2021}\vspace{.5mm}\\%
                \textbf{Executive Committee}, Mathematics and Computation Division, ANS  \hfill \textbf{2020--2021}\vspace{.5mm}\\%
                \textbf{Vice Chair}, Nonproliferation and Policy Division, ANS  \hfill \textbf{2019--2020}\vspace{.5mm}\\%
    \textbf{Past Chair} \emph{(ex officio)}, Fuel Cycle \& Waste Management Division, ANS  \hfill \textbf{2016--2017}\vspace{.5mm}\\%
                \textbf{Co-Organizer}, Technical Workshop on Fuel Cycle Simulation \hfill \textbf{2017}\vspace{.5mm}\\%
                \textbf{Technical Program Committee}, IHLRWM Conference \hfill \textbf{2017}\vspace{.5mm}\\%
                \textbf{Chair}, Fuel Cycle \& Waste Management Division, ANS  \hfill \textbf{2016--2017}\vspace{.5mm}\\%
                \textbf{Vice Chair}, Fuel Cycle \& Waste Management Division, ANS  \hfill \textbf{2015--2016}\vspace{.5mm}\\%
                \textbf{Chair}, Steering Committee, Software Carpentry Foundation   \hfill \textbf{2014--2015}\vspace{.5mm}\\%
                \textbf{Secretary--Treasurer}, Fuel Cycle \& Waste Management Division, ANS  \hfill \textbf{2013--2015}\vspace{.5mm}\\%
                \textbf{Secretary}, Young Members Group, ANS  \hfill \textbf{2013--2014}\vspace{.5mm}\\%
                \textbf{Technical Program Co-Chair}, SciPy, Scientific Python Conference   \hfill \textbf{2013--2014}\vspace{.5mm}\\%
                \textbf{Member}, Next Generation Leadership Committee, Waste Management Symposium  \hfill \textbf{2013--2014}\vspace{.5mm}\\%
                \textbf{Moderator, Organizer, Panelist}, inSCIght Scientific Computing Podcast  \hfill \textbf{2011--2013}\vspace{.5mm}\\%
                \textbf{Co-Founder}, Nuclear Pride, LGBTQA Organization  \hfill \textbf{2011--2013}\vspace{.5mm}\\%
                \textbf{Co-Founder, Treasurer, President}, Hacker Within Scientific Computing Group  \hfill \textbf{2008--2011}\vspace{.5mm}\\%
                \textbf{Governor, Treasurer}, University of Wisconsin ANS student section  \hfill \textbf{2008--2010}\vspace{.5mm}%
    %__________________________________________________________________________________________________________________
    \section{\mysidestyle Departmental\\Service}
                \textbf{Faculty Advisor}, UIUC ANS Student Section \hfill \textbf{2016--present}\vspace{.5mm}\\%
                \textbf{Undergraduate Committee},\hfill \textbf{2019--present}\vspace{.5mm}\\%
                \textbf{Graduate Committee}, Qualifying Exam Sub-Committee \hfill \textbf{2017-2019}\vspace{.5mm}\\%
                                             Admissions Sub-Committee \hfill \textbf{Spring 2017}\vspace{.5mm}\\%
                                             Admissions Sub-Committee \hfill \textbf{Fall 2016}\vspace{.5mm}\\%
                \textbf{Advisory Committee}, \hfill \textbf{2017--2018}\vspace{.5mm}\\%
                \textbf{Faculty Search Committee}, \hfill \textbf{2017--2018}\vspace{.5mm}\\%
                \textbf{Faculty Advisor}, UIUC WiN Student Section \hfill \textbf{2017--2018}\vspace{.5mm}\\%
    \section{\mysidestyle College\\Service}
                \textbf{Member}, Instructional Facility Working Group \hfill \textbf{2017--2018}\vspace{.5mm}\\%
                \textbf{Faculty Advisor}, UIUC CSE The Hacker Within Scientific Computing Group \hfill \textbf{2016--2017}\vspace{.5mm}\\%
    \section{\mysidestyle Campus\\Service}
                \textbf{Steering Committee Member}, Illinois Data Science Initiative \hfill \textbf{2018}\vspace{.5mm}\\%
                \textbf{Hack Mentor}, Hack Illinois \hfill \textbf{2017}\vspace{.5mm}\\%

    %__________________________________________________________________________________________________________________
    % Consulting
    \section{\mysidestyle Consulting}


    \textbf{Thomas Edison State University} Trenton, NJ \hfill
    \textbf{2018-2019}\\
    \textsl{Subject Matter Expert} \\
    Institute of Nuclear Power Operations (INPO) Academic Program Review\\


    %__________________________________________________________________________________________________________________
    % References

%\section{\mysidestyle References}
%\texsl{Available upon request}

%______________________________________________________________________________________________________________________


    %__________________________________________________________________________________________________________________
\end{resume}

\end{document}


%______________________________________________________________________________________________________________________
% EOF

